Figures

### 2020-01-07 manuscript/figures.Rmd
add contrasts figures

<!-- # exploratory analyses -->

```{r heatmap, fig.cap = "Heatmap caption.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_heatmap-1.pdf")
```

<!-- # hypsography classification figure (panelized by state) -->
```{r hypsography, fig.cap = "Hypsography classification by state.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_hypsography-1.pdf")
```

>>>>

```{r heatmap, fig.cap = "Correlation matrix heatmap.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_heatmap-1.pdf")
```

```{r hypsography, fig.cap = "Hypsography classification by state.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_hypsography-1.pdf")
```

```{r contrasts_depth, fig.cap = "Lake maximum depth by categorical variables.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_contrasts_depth-1.pdf")
```

```{r contrasts_tally, fig.cap = "Number of lakes by categories.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_contrasts_tally-1.pdf")
```
